\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-04-21 doc/sw-system.tex
adding graphics path for ease of submission to arxivs

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/sw-screengrab-marker+feedback.png}
\caption{Screenshot of the \SW classification interface.}
\label{fig:screenshot}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure*}%[!ht]
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/4.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/5.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/6.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/7.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\caption{Typical \SW ``sims'' from the \StageTwo training set. The top right-hand corner insets indicate the
location of the simulated lens in each of these training images. Users needed to
click on these specific features in order to make a correct classification.}
\label{fig:training-gallery:sims}
\end{figure*}

\begin{figure*}%[!ht]
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/0_ASW0009dgn.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/1_ASW0009dgo.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/2_ASW0009dgy.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/3_ASW0009dh0.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\caption{Typical \SW ``duds'' from the \StageTwo training set. All of these
subjects were correctly classified by the community as not likely to contain
gravitational lenses.} \label{fig:training-gallery:duds}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_probabilities.png}
\caption{Typical \SW agent confusion matrix elements. At a particular
snapshot, 200 randomly-selected agents are shown distributed over the unit plane, with a
tendency to move towards the ``astute'' region in the upper right hand
quadrant as each agent's volunteer views more images. Yellow point size is
proprtional to the number of images classified; green point size shows
agent-perceived ``skill.''}
\label{fig:swap:agent-probabilities}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure}
%\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_histories.png}
%\caption{Typical \SW agent histories. The ``skill'' of the  same 200 random
%agents  as in \Fref{fig:swap:agent-probabilities} is plotted in green as a function
%of the number  of subjects classified (``effort''). The yellow histogram in
%the background shows the distribution of effort.}
%\label{fig:swap:agent-histories}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_trajectories.png}
\caption{Typical \SW \StageOne subject trajectories. Top: 200 randomly-selected
subjects drift downwards as they are classified, while being nudged left and
right in probability by the agents as they interpret the volunteers input. The
dotted vertical lines show (left to right) the retirement threshold, prior
probability, and the detection threshold. Different colours denote the different
kinds of subject. Bottom panel: histograms of all the subject probabilities
computed to date, sub-divided by subject kind.}
\label{fig:swap:subject-trajectories}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\begin{minipage}{0.45\linewidth}
  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage1_ROC.pdf}
\end{minipage}\hfill
\begin{minipage}{0.45\linewidth}
  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage2_ROC.pdf}
\end{minipage}
\caption{Receiver operating characteristic curves for the \SW system, using
the \cfhtls training set. Left: \StageOne, right: \StageTwo. Insets show a
magnified view of the top lefthand corner of each plot. Linestyles illustrate
the agent properties (initial confusion matrix elements, learning or not)
discussed in the text, as well as the difference between the online and offline
analyses. The \StageTwo sample was defined using the online \StageOne results
(solid blue curve), while the offline analysis was chosen for the final
\StageTwo results (dot-dashed orange curve). }
\label{fig:results:sample:roc}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=\linewidth]{sw-system-figs/completeness_purity_simple.pdf}
\caption{Completeness-estimated purity curves for the \sw system, using
the \cfhtls training set.}
\label{fig:results:sample:CP}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/all_skill_contribution_experience_education.pdf}
\caption{Key properties and contributions of the \SW \StageOne crowd.
Plotted are the 1-D
and 2-D smoothed marginalized distributions for  the logarithms of the
properties of the agents described in the text. The contours
contain 68\%, 95\% and 99\% of the distributions.}
\label{fig:crowd:cornerplot}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_contrib_cumul.pdf}
\caption{Cumulative distributions of the contributions made by the agents: 90\%
of the contribution was made by the highest contributing 1\% of the crowd at
\StageOne (blue), and the highest contributing  7\% of the crowd at \StageTwo
(orange). The \StageOne agents are shown in blue, the \StageTwo agents in
orange. ``Experienced volunteers'' classified 10 or more training subjects.}
\label{fig:crowd:cumulplot}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_skill_cumul.pdf}
\caption{Broad cumulative distributions of agent skill:
the most skilled 20\% of the crowd only possess around 80\% of the skill,
at \StageOne. The \StageOne agents
are shown in blue, the \StageTwo agents in orange. ``Experienced volunteers''
classified 10 or more training subjects.}
\label{fig:crowd:cumulskillplot}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=\linewidth]{sw-system-figs/rate_classification.pdf}
\caption{Fractional classification rate in the \SW \cfhtls survey. Fractional classification rate is the number
of classifications per unit time, divided by the final total number of
classifications. Fractional survey time is the time elapsed since the beginning
of the survey, divided by the total length of the survey. The unit of time in
the fractional  classification rate is one survey, so that the curves in
integrals under the curves are both one. }
\label{fig:results:speed}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\begin{minipage}{\linewidth}
  \begin{minipage}[t]{0.47\linewidth}
    \begin{minipage}{0.46\linewidth}
      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0008wyp_gri.png}
    \end{minipage}\hfill
    \begin{minipage}{0.50\linewidth}
      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0008wyp_stage2_trajectory.png}
    \end{minipage}
  \end{minipage}\hfill
  \begin{minipage}[t]{0.47\linewidth}
    \begin{minipage}{0.46\linewidth}
      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0006rkx_gri.png}
    \end{minipage}\hfill
    \begin{minipage}{0.50\linewidth}
      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0006rkx_stage1_trajectory.png}
    \end{minipage}
  \end{minipage}
\end{minipage}

@@

\begin{minipage}{\linewidth}
  \begin{minipage}[t]{0.47\linewidth}
    \begin{minipage}{0.46\linewidth}
      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0000fgj_gri.png}
    \end{minipage}\hfill
    \begin{minipage}{0.50\linewidth}
      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0000fgj_stage1_trajectory.png}
    \end{minipage}
  \end{minipage}\hfill
  \begin{minipage}[t]{0.47\linewidth}
    \begin{minipage}{0.46\linewidth}
      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0003j2s_gri.png}
    \end{minipage}\hfill
    \begin{minipage}{0.50\linewidth}
      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0003j2s_stage1_trajectory.png}
    \end{minipage}
  \end{minipage}
\end{minipage}
\caption{Illustrative examples of
false negatives (blue) and false positives (red) from the classification of
the \SW \cfhtls training set. The trajectory plot for each of the 4 subjects is
shown to the right of its image. Lefthand panels show the most common types of
trajectories: short step random walks resulting from no high skill classifiers
viewing the subject. The righthand panels show examples where higher skill
classifiers have been involved, causing random walks with longer step lengths
(top) and catastrophic mis-classifications (bottom right). Note that both these
subjects were {\it very nearly} detected but didn't quite reach the threshold
set (marked by the blue dashed line). Insets for the false
negatives show the lens feature. The inset for the lower righthand panel shows
where most users believed a lens was located. There is no corresponding inset
for the lower left panel because no particular feature stood out to users.
Instead, users clicked many different features.}
\label{fig:discuss:performance:trajectories}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/stage2_veteran_contribution.pdf}
\caption{\StageTwo classifier skill, as a function of their \StageOne skill.
Veterans from \StageOne  are shown in blue, while new volunteers are shown in
orange. Point size is proportional to the total contribution made,
while dashed lines are drawn at the mean values for each sample.}
\label{fig:discuss:performance:stage1vstage2}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{figure}
% \centering\includegraphics[width=0.9\linewidth]{sw-system-figs/early_vs_final_skill.png}
% \caption{Predictability of final skill from early skill (after 10 training
% classifications) in \StageOne agents. The dashed lines enclose 649 agents with
% early skill greater than 0.1
% who retain final skill of greater than 0.05. Point size is proportional to
% contribution (plus a constant).}
% \label{fig:crowd:skillprediction}
% \end{figure}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Having seen the importance of the high skill volunteers at both \StageOne and
% \StageTwo, we might ask, can we predict agent skill after, say, the volunteer
% has experienced 10 training subjects? In \Fref{fig:crowd:skillprediction} we
% plot this ``early skill'' against final skill, for all experienced \StageOne
% volunteers. The majority of the crowd shows little correlation, but at the
% high early skill end, some predictability appears. The 649 experienced \StageOne
% volunteers who had early skill greater than 0.1 went on to attain a mean
% final skill of 0.22, with 97\% remaining at skill 0.05 or higher. This
% suggests that it might be worth tracking volunteers' skill as a project
% progresses, in order to encourage those showing an aptitude for the task to
% take part in the more difficult activities, such as \StageTwo refinement.
% However, this would not have done a very good job at identifying the
% volunteers who went on to make the largest contributions: the point size in
% \Fref{fig:crowd:skillprediction} is proportional to contribution (plus a constant):
% many of the highest contributors showed relatively low skill early on.

>>>>

\graphicspath{{./}{sw-system-figs/}{sw-system-figs/gallery/}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering\includegraphics[width=0.9\linewidth]{sw-screengrab-marker+feedback.png}
\caption{Screenshot of the \SW classification interface.}
\label{fig:screenshot}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure*}%[!ht]
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=4.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=5.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=6.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=7.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\caption{Typical \SW ``sims'' from the \StageTwo training set. The top right-hand corner insets indicate the
location of the simulated lens in each of these training images. Users needed to
click on these specific features in order to make a correct classification.}
\label{fig:training-gallery:sims}
\end{figure*}

\begin{figure*}%[!ht]
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=0_ASW0009dgn.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=1_ASW0009dgo.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=2_ASW0009dgy.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=3_ASW0009dh0.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\caption{Typical \SW ``duds'' from the \StageTwo training set. All of these
subjects were correctly classified by the community as not likely to contain
gravitational lenses.} \label{fig:training-gallery:duds}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{CFHTLS_2013-10-29_10:16:35_probabilities.png}
\caption{Typical \SW agent confusion matrix elements. At a particular
snapshot, 200 randomly-selected agents are shown distributed over the unit plane, with a
tendency to move towards the ``astute'' region in the upper right hand
quadrant as each agent's volunteer views more images. Yellow point size is
proprtional to the number of images classified; green point size shows
agent-perceived ``skill.''}
\label{fig:swap:agent-probabilities}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure}
%\centering\includegraphics[width=0.9\linewidth]{CFHTLS_2013-10-29_10:16:35_histories.png}
%\caption{Typical \SW agent histories. The ``skill'' of the  same 200 random
%agents  as in \Fref{fig:swap:agent-probabilities} is plotted in green as a function
%of the number  of subjects classified (``effort''). The yellow histogram in
%the background shows the distribution of effort.}
%\label{fig:swap:agent-histories}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{CFHTLS_2013-10-29_10:16:35_trajectories.png}
\caption{Typical \SW \StageOne subject trajectories. Top: 200 randomly-selected
subjects drift downwards as they are classified, while being nudged left and
right in probability by the agents as they interpret the volunteers input. The
dotted vertical lines show (left to right) the retirement threshold, prior
probability, and the detection threshold. Different colours denote the different
kinds of subject. Bottom panel: histograms of all the subject probabilities
computed to date, sub-divided by subject kind.}
\label{fig:swap:subject-trajectories}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\begin{minipage}{0.45\linewidth}
  \centering\includegraphics[width=\linewidth]{stage1_ROC.pdf}
\end{minipage}\hfill
\begin{minipage}{0.45\linewidth}
  \centering\includegraphics[width=\linewidth]{stage2_ROC.pdf}
\end{minipage}
\caption{Receiver operating characteristic curves for the \SW system, using
the \cfhtls training set. Left: \StageOne, right: \StageTwo. Insets show a
magnified view of the top lefthand corner of each plot. Linestyles illustrate
the agent properties (initial confusion matrix elements, learning or not)
discussed in the text, as well as the difference between the online and offline
analyses. The \StageTwo sample was defined using the online \StageOne results
(solid blue curve), while the offline analysis was chosen for the final
\StageTwo results (dot-dashed orange curve). }
\label{fig:results:sample:roc}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=\linewidth]{completeness_purity_simple.pdf}
\caption{Completeness-estimated purity curves for the \sw system, using
the \cfhtls training set.}
\label{fig:results:sample:CP}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering\includegraphics[width=0.9\linewidth]{all_skill_contribution_experience_education.pdf}
\caption{Key properties and contributions of the \SW \StageOne crowd.
Plotted are the 1-D
and 2-D smoothed marginalized distributions for  the logarithms of the
properties of the agents described in the text. The contours
contain 68\%, 95\% and 99\% of the distributions.}
\label{fig:crowd:cornerplot}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{crowd_contrib_cumul.pdf}
\caption{Cumulative distributions of the contributions made by the agents: 90\%
of the contribution was made by the highest contributing 1\% of the crowd at
\StageOne (blue), and the highest contributing  7\% of the crowd at \StageTwo
(orange). The \StageOne agents are shown in blue, the \StageTwo agents in
orange. ``Experienced volunteers'' classified 10 or more training subjects.}
\label{fig:crowd:cumulplot}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{crowd_skill_cumul.pdf}
\caption{Broad cumulative distributions of agent skill:
the most skilled 20\% of the crowd only possess around 80\% of the skill,
at \StageOne. The \StageOne agents
are shown in blue, the \StageTwo agents in orange. ``Experienced volunteers''
classified 10 or more training subjects.}
\label{fig:crowd:cumulskillplot}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=\linewidth]{rate_classification.pdf}
\caption{Fractional classification rate in the \SW \cfhtls survey. Fractional classification rate is the number
of classifications per unit time, divided by the final total number of
classifications. Fractional survey time is the time elapsed since the beginning
of the survey, divided by the total length of the survey. The unit of time in
the fractional  classification rate is one survey, so that the curves in
integrals under the curves are both one. }
\label{fig:results:speed}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\begin{minipage}{\linewidth}
  \begin{minipage}[t]{0.47\linewidth}
    \begin{minipage}{0.46\linewidth}
      \centering\includegraphics[width=\linewidth]{ASW0008wyp_gri.png}
    \end{minipage}\hfill
    \begin{minipage}{0.50\linewidth}
      \centering\includegraphics[width=\linewidth]{ASW0008wyp_stage2_trajectory.png}
    \end{minipage}
  \end{minipage}\hfill
  \begin{minipage}[t]{0.47\linewidth}
    \begin{minipage}{0.46\linewidth}
      \centering\includegraphics[width=\linewidth]{ASW0006rkx_gri.png}
    \end{minipage}\hfill
    \begin{minipage}{0.50\linewidth}
      \centering\includegraphics[width=\linewidth]{ASW0006rkx_stage1_trajectory.png}
    \end{minipage}
  \end{minipage}
\end{minipage}

@@

\begin{minipage}{\linewidth}
  \begin{minipage}[t]{0.47\linewidth}
    \begin{minipage}{0.46\linewidth}
      \centering\includegraphics[width=\linewidth]{ASW0000fgj_gri.png}
    \end{minipage}\hfill
    \begin{minipage}{0.50\linewidth}
      \centering\includegraphics[width=\linewidth]{ASW0000fgj_stage1_trajectory.png}
    \end{minipage}
  \end{minipage}\hfill
  \begin{minipage}[t]{0.47\linewidth}
    \begin{minipage}{0.46\linewidth}
      \centering\includegraphics[width=\linewidth]{ASW0003j2s_gri.png}
    \end{minipage}\hfill
    \begin{minipage}{0.50\linewidth}
      \centering\includegraphics[width=\linewidth]{ASW0003j2s_stage1_trajectory.png}
    \end{minipage}
  \end{minipage}
\end{minipage}
\caption{Illustrative examples of
false negatives (blue) and false positives (red) from the classification of
the \SW \cfhtls training set. The trajectory plot for each of the 4 subjects is
shown to the right of its image. Lefthand panels show the most common types of
trajectories: short step random walks resulting from no high skill classifiers
viewing the subject. The righthand panels show examples where higher skill
classifiers have been involved, causing random walks with longer step lengths
(top) and catastrophic mis-classifications (bottom right). Note that both these
subjects were {\it very nearly} detected but didn't quite reach the threshold
set (marked by the blue dashed line). Insets for the false
negatives show the lens feature. The inset for the lower righthand panel shows
where most users believed a lens was located. There is no corresponding inset
for the lower left panel because no particular feature stood out to users.
Instead, users clicked many different features.}
\label{fig:discuss:performance:trajectories}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{stage2_veteran_contribution.pdf}
\caption{\StageTwo classifier skill, as a function of their \StageOne skill.
Veterans from \StageOne  are shown in blue, while new volunteers are shown in
orange. Point size is proportional to the total contribution made,
while dashed lines are drawn at the mean values for each sample.}
\label{fig:discuss:performance:stage1vstage2}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{figure}
% \centering\includegraphics[width=0.9\linewidth]{early_vs_final_skill.png}
% \caption{Predictability of final skill from early skill (after 10 training
% classifications) in \StageOne agents. The dashed lines enclose 649 agents with
% early skill greater than 0.1
% who retain final skill of greater than 0.05. Point size is proportional to
% contribution (plus a constant).}
% \label{fig:crowd:skillprediction}
% \end{figure}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Having seen the importance of the high skill volunteers at both \StageOne and
% \StageTwo, we might ask, can we predict agent skill after, say, the volunteer
% has experienced 10 training subjects? In \Fref{fig:crowd:skillprediction} we
% plot this ``early skill'' against final skill, for all experienced \StageOne
% volunteers. The majority of the crowd shows little correlation, but at the
% high early skill end, some predictability appears. The 649 experienced \StageOne
% volunteers who had early skill greater than 0.1 went on to attain a mean
% final skill of 0.22, with 97\% remaining at skill 0.05 or higher. This
% suggests that it might be worth tracking volunteers' skill as a project
% progresses, in order to encourage those showing an aptitude for the task to
% take part in the more difficult activities, such as \StageTwo refinement.
% However, this would not have done a very good job at identifying the
% volunteers who went on to make the largest contributions: the point size in
% \Fref{fig:crowd:skillprediction} is proportional to contribution (plus a constant):
% many of the highest contributors showed relatively low skill early on.
